% Clever Algorithms: Machine Learning Algorithm Selection

% The Clever Algorithms Project: http://www.CleverAlgorithms.com
% (c) Copyright 2011 Jason Brownlee. Some Rights Reserved. 
% This work is licensed under a Creative Commons Attribution-Noncommercial-Share Alike 2.5 Australia License.

\documentclass[a4paper, 11pt]{article}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{url}
\usepackage[pdftex,breaklinks=true,colorlinks=true,urlcolor=blue,linkcolor=blue,citecolor=blue,]{hyperref}
\usepackage{geometry}
\geometry{verbose,a4paper,tmargin=25mm,bmargin=25mm,lmargin=25mm,rmargin=25mm}

% Dear template user: fill these in
\newcommand{\myreporttitle}{Clever Algorithms}
\newcommand{\myreportsubtitle}{Machine Learning Algorithm Selection}
\newcommand{\myreportauthor}{Jason Brownlee}
\newcommand{\myreportemail}{jasonb@CleverAlgorithms.com}
\newcommand{\myreportwebsite}{http://www.CleverAlgorithms.com}
\newcommand{\myreportproject}{The Clever Algorithms Project\\\url{\myreportwebsite}}
\newcommand{\myreportdate}{20110213}
\newcommand{\myreportfulldate}{\today}
\newcommand{\myreportversion}{1}
\newcommand{\myreportlicense}{\copyright\ Copyright 2011 Jason Brownlee. Some Rights Reserved. This work is licensed under a Creative Commons Attribution-Noncommercial-Share Alike 2.5 Australia License.}

% leave this alone, it's templated baby!
\title{{\myreporttitle}: {\myreportsubtitle}\footnote{\myreportlicense}}
\author{\myreportauthor\\{\myreportemail}\\\small\myreportproject}
\date{\myreportfulldate\\{\small{Technical Report: CA-TR-{\myreportdate}-\myreportversion}}}
\begin{document}
\maketitle

% write a summary sentence for each major section
\section*{Abstract} 
% project
The Clever Algorithms: Machine Learning project intends to describe a large number of methods from the field of Machine Learning in a complete, consistent, and centralized way, such that the descriptions are usable, accessible, and understandable.
% this report
This report provides...


\begin{description}
	\item[Keywords:] {\small\texttt{Clever Algorithms, Taxonomy, Algorithm Selection, Data Driven}}
\end{description} 

%
% Introduction
%
\section{Introduction}
\label{sec:introduction}
% project
The Clever Algorithms: Machine Learning project intends to describe a large number of methods from the field of Machine Learning in a complete, consistent, and centralized way, such that the descriptions are usable, accessible, and understandable \cite{Brownlee2011a}.
% the old method
A previous study...
% this report
This report provides...


%
% Algorithm Organization
%
\section{Algorithm Organization}
\label{sec:organization}
This section reviews the ways in which machine learning algorithms are organized in popular books and software libraries. This review is expected to provide the basis for an organization or taxonomy to be adopted in the clever algorithms project.

% Books
\subsection{Books}
Books...


% Software
\subsection{Software}
This section reviews the algorithms provided by popular open source machine learning software, and summarizes the groupings or taxonomies used to organize the provided algorithms.

WEKA is...
Table~\ref{tab:weka} provides a summary of the grouping of algorithms provided in the WEKA machine learning workbench software library. 

\begin{table}[htp]
	\centering\footnotesize
		\begin{tabularx}{\textwidth}{lX}
		\toprule
		\textbf{Group} & \textbf{Algorithm Name} \\ 
		\toprule
		bayes & b \\
		functions & b \\
		lazy & b \\
		bayes & b \\
		meta & b \\
		mi & b \\
		misc & b \\
		rules & b \\
		trees & b \\
		clusterers & b \\
		associate & b \\
		attribute selection & b \\
		\bottomrule
		\end{tabularx}	
	\caption{summary of algorithms provided in WEKA and their grouping.}
	\label{tab:weka}
\end{table}


%
% Algorithm Assessment
%
\section{Algorithm Assessment}
\label{sec:assessment}
This section assesses a listing of known machine learning algorithms to determine their commonality and popularity. It is expected that the results from this section will provide the basis for selecting the algorithms to be described in the clever algorithms project.

% Methodology
\subsection{Methodology}

% Results
\subsection{Results}

% Analysis
\subsection{Analysis}



%
% Selected Algorithms
%
\section{Selected Algorithms}
\label{sec:selected}
This section provides a preliminary description of the machine learning algorithms that will be described in the clever algorithms project. This list includes a summary of the chosen algorithm taxonomy that will be used to organize those algorithms that are described. 

% Adopted Taxonomy
\subsection{Taxonomy}
the taxonomy


% Adopted Taxonomy
\subsection{Algorithms}
the algorithms



%
% Conclusions
%
\section{Conclusions}
\label{sec:conclusions}
todo...




% 
% Contribute
% 
\section{Contribute}
\label{sec:contribute}
% advanced 
Are you an expert in this field and know some facts that could improve the algorithm description for all?
% incentive
Do you want to get that warm feeling from contributing to an open source project? 
Do you want to see your name as an acknowledgment in print?

%  ideal
Two pillars of this effort are 1) that the best domain experts are people outside of the project, and 2) that this work is subjected to continuous improvement. 
% advice
Please help to make this work less wrong by emailing the author `\myreportauthor' at \url{\myreportemail} or visit the project website at \url{\myreportwebsite}.

% bibliography
\bibliographystyle{plain}
\bibliography{../bibtex}

\end{document}
% EOF
