% The Clever Algorithms Project: http://www.CleverAlgorithms.com
% (c) Copyright 2013 Jason Brownlee. Some Rights Reserved. 
% This work is licensed under a Creative Commons Attribution-Noncommercial-Share Alike 2.5 Australia License.

% This is a chapter

% Argument and background information the user requires to read and understand the book
\chapter{Introduction}
\label{chap:intro}
\begin{bibunit}

% welcome
\emph{Welcome to Clever Algorithms!} This is a handbook of recipes for computational problem solving techniques from the field of Statistical Machine Learning. 
% they are for using
Clever Algorithms are interesting, practical, and fun to learn about and implement.
% briefly the audience
Research scientists may be interested in browsing algorithm in search of an interesting system to investigate. Developers and software engineers may compare various problem solving algorithms and technique-specific guidelines. Practitioners, students, and interested amateurs may implement state-of-the-art algorithms to address business or scientific needs, or simply play with the fascinating systems they represent.

% briefly book overview
This introductory chapter provides relevant background information on Machine Learning and Algorithms. The core of the book provides a large corpus of algorithms presented in a complete and consistent manner. The final chapter covers some advanced topics to consider once a number of algorithms have been mastered. This book has been designed as a reference text, where specific techniques are looked up, or where the algorithms across whole fields of study can be browsed, rather than being read cover-to-cover. This book is an algorithm handbook and a technique guidebook, and I hope you find something useful.

% sections
\input{c_introduction/machine_learning}
\input{c_introduction/problem_domains}
\input{c_introduction/considerations}
\input{c_introduction/organization}
\input{c_introduction/further_reading}

% bib
\renewcommand{\bibsection}{\section{\bibname}}
\putbib
\end{bibunit}